Stock forecasting algorithms and their usage

### 2015-06-12 Paper_self.tex
little changes to paper

% author names and affiliations
% use a multiple column layout for up to three different
% affiliations
\author{\IEEEauthorblockN{Marc Misoch}
\IEEEauthorblockA{Institute of Computer Science\\University of Applied Science\\
Mannheim, Germany\\
Email: marc.misoch@gmail.com}
\and
\IEEEauthorblockN{David Marquant}
\IEEEauthorblockA{Institute of Computer Science\\University of Applied Science\\
Mannheim, Germany\\
Email: david.ma@live.com}
}

@@

The following table shows the results of applying different machine learning techniques to stock data. All used methods achieve similar results. The accuracy of the prediction is barely higher than the probability of a coin flip. But none of the cases do have a prediction accuracy below 50\%. The algorithm, as it is, should not be used without further improvements and refinement.

\begin{center}
\begin{tabularx}{0.5\textwidth}{|X|X|X|X|X|X|}
\hline
{} &     
\^{}AXJO\footnote{Australia ASX-200} &     
\^{}FCHI\footnote{Paris CAC 40} &     
\^{}FTSE\footnote{London FTSE-100} &    
\^{}GDAXI\footnote{Frankfurt DAX} & 
\^{}IXIC\footnote{NASDAQ Composite}\\
\hline
LDA &  0.501 &  0.541 &  0.527 &  0.555 & 0.571\\
LR  &  0.501 &  0.541 &  0.527 &  0.555 & 0.571\\
QDA &  0.541 &  0.513 &  0.519 &  0.539 & 0.575\\
\hline
\end{tabularx}
\\[5pt]
Table 3. Results of Supervised Learning Algorithms
\end{center}

@@

>>>>

% author names and affiliations
% use a multiple column layout for up to three different
% affiliations
\author{\IEEEauthorblockN{Marc Misoch}
\IEEEauthorblockA{Institute of Computer Science\\University of Applied Science\\
Mannheim, Germany\\
Email: marc.misoch@stud.hs-mannheim.de}
\and
\IEEEauthorblockN{David Marquant}
\IEEEauthorblockA{Institute of Computer Science\\University of Applied Science\\
Mannheim, Germany\\
Email: david.marquant@stud.hs-mannheim.de}
}

@@

The following table shows the results of applying different machine learning techniques to stock data. All used methods achieve similar results. The accuracy of the prediction is barely higher than the probability of a coin flip. But none of the cases do have a prediction accuracy below 50\%. The algorithm, as it is, should not be used without further improvements and refinement. 
\\
\begin{center}
\begin{tabularx}{0.5\textwidth}{|X|X|X|X|X|X|}
\hline
{} &     
\^{}AXJO\footnote{Australia ASX-200} &     
\^{}FCHI\footnote{Paris CAC 40} &     
\^{}FTSE\footnote{London FTSE-100} &    
\^{}GDAXI\footnote{Frankfurt DAX} & 
\^{}IXIC\footnote{NASDAQ Composite}\\
\hline
LDA &  0.501 &  0.541 &  0.527 &  0.555 & 0.571\\
LR  &  0.501 &  0.541 &  0.527 &  0.555 & 0.571\\
QDA &  0.541 &  0.513 &  0.519 &  0.539 & 0.575\\
\hline
\end{tabularx}
\\[5pt]
Table 3. Results of Supervised Learning Algorithms
\end{center}

@@

  \bibitem{Khaled}
  Stock price prediction using genetic algorithms and evolution
strategies
Ganesh Bonde, Rasheed Khaled

\bibitem{zhang}
Stock Market Forecasting Using Machine Learning Algorithms
Shunrong Shen, Haomiao Jiang, Tongda Zhang

\bibitem{Tang}
Stock Price Forecasting by Combining News Mining and Time Series Analysis
Xiangyu Tang, Chunyu Yang, Jie Zhou
